
---
title: "The Relation between Representational Competence and Conceptual Knowledge in Physics"
output: 
  html_document: 
    df_print: default
    highlight: espresso
    keep_md: yes
    smart: no
    theme: spacelab
editor_options: 
  chunk_output_type: console
---
author: ""
output:
  html_document:
    theme: cerulean
encoding: UTF-8
editor_options: 
  chunk_output_type: console
---

<style>
pre {
  overflow-x: auto;
}
pre code {
  word-wrap: normal;
  white-space: pre;
}
</style>

---

# {.tabset}

```{r}

setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

library(readxl)
library(tidyverse)
library(foreign)
library(tidyverse)
library(GGally)
library(lavaan)
library(TAM)
library(WrightMap)
library(psych)
library(tidyLPA)
library(magrittr)
library(cluster)
library(factoextra)
library(writexl)
library(readxl)
library(ShinyItemAnalysis)
library(MplusAutomation)
library(confintr)
library(DescTools)

##set manual ggally-options for plotting
my_descriptivesfunction <- function(data, mapping, ...){
  p <- ggplot(data = data, mapping = mapping) + 
    geom_point(position = position_jitter(), shape = 21, colour = "blue2", fill = "white") + 
    geom_smooth(method = loess, fill = "red", color="darkblue", se = FALSE, ...) +
    geom_smooth(method = lm, fill="blue", color = "darkred", ...)
  p
}


theme_pety <- function(base_size = 10, base_family = "") {
  theme(text = element_text(size = 16), #Larger text font size
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(colour="black"), #x-Axis text colour
        axis.text.y = element_text(colour="black")) #y-Axis text colour
}

load("CESAR03.Rdata")

table(CESAR03$TeacherEd_MINT)

#RQ1: Do we find correlations in all samples?

#Sample 1: Teacher education Saarbrücken
CESAR03 %>% filter(subsample == "1") %>% select(Repko_score, Konzept_score) %>% cor() #.37
#Sample 2: TU Kaiserslautern Mech Eng, Elec Eng a.o.
CESAR03 %>% filter(subsample == "2") %>% select(Repko_score, Konzept_score) %>% cor() #.58
#Sample 3: ETH Zurich; Environmental Sciences a.o.
CESAR03 %>% filter(subsample == "3") %>% select(Repko_score, Konzept_score) %>% cor() #.36
#Sample 4: ETH Zurich; Physics a.o.
CESAR03 %>% filter(subsample == "4") %>% select(Repko_score, Konzept_score) %>% cor() #.55

CESAR03 %>%
  mutate(Sample = fct_recode(factor(subsample),
                             "Teacher Education SU" = "1",
                             "Engineering TUK" = "2",
                             "Environmental Science ETH" = "3",
                             "Physics ETH" = "4")) %>%
  ggplot(aes(x = Repko_score, y = Konzept_score)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.2), color = "darkblue", shape = 21, fill = "white") +
  geom_smooth(method = "lm") +

  geom_smooth(color = "darkred", size = 1, se = FALSE, span = 0.75) +
  scale_y_continuous("Conceptual knowledge (max. = 12)",
                     limits = c(-1, 13),
                     breaks = c(0, 2, 4, 6, 8, 10, 12)) +
  scale_x_continuous("Representational competence (max. = 12)",
                     limits = c(-1, 13),
                     breaks = c(0, 2, 4, 6, 8, 10, 12)) +
  theme_pety() +
  theme(legend.position = "none") +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~ Sample)

ggsave("RQ1_Scatter_persample.png", width = 8, height = 6, dpi = 450)

#RQ3: Export data object with focal profile variables and covariates for latent profile analyses via MplusAutomation
CESAR03 %>% select(ID, Repko_score, Konzept_score,
             subsample, male, leit_exp, Teacherstudent, MINT) %>%
  mutate(Teacherstudent = as.character(fct_recode(Teacherstudent,
                                     "0" = "Non-TeachEd",
                                     "1" = "TeachEd")),
         MINT = as.character(fct_recode(MINT,
                                        "0" = "Non-MINT",
                                        "1" = "MINT"))) %>%
  write.table("CESAR03.dat", sep = "\t", row.names = FALSE, col.names = FALSE, na = "9999")

## With robust scaled profiling variables
hist(log(CESAR03$Repko_score))
hist(CESAR03$Repko_score)
describe(CESAR03$Repko_score)
describe(log(CESAR03$Repko_score + 1))
describe(CESAR03$Konzept_score)
describe(log(CESAR03$Konzept_score + 1))
describe(CESAR03$Repko_score^2)
CESAR03 %>% select(ID, Repko_score, Konzept_score,
             subsample, male, leit_exp, Teacherstudent, MINT) %>%
 # mutate(Repko_score = scale(Repko_score)[,1],
#         Konzept_score = scale(Konzept_score)[,1]) %>%
      mutate(Konzept_score = log(Konzept_score + 1)) %>%
    # mutate(Repko_score = log(Repko_score + 1),
    #      Konzept_score = log(Konzept_score + 1)) %>%
    mutate(Repko_score = DescTools::RobScale(Repko_score),
         Konzept_score = DescTools::RobScale(Konzept_score)) %>%
#  mutate(Repko_score = percent_rank(Repko_score),
#         Konzept_score = percent_rank(Konzept_score)) %>%    
  mutate(Teacherstudent = as.character(fct_recode(Teacherstudent,
                                     "0" = "Non-TeachEd",
                                     "1" = "TeachEd")),
         MINT = as.character(fct_recode(MINT,
                                        "0" = "Non-MINT",
                                        "1" = "MINT"))) %>%
  write.table("CESAR03_robscaled.dat", sep = "\t", row.names = FALSE, col.names = FALSE, na = "9999")

```

## Analyses paper

Research questions 1-2:
See Mplus inputs and outputs

Research questions 3-5:

(3) To what degree do latent profiles of representational competence and conceptual knowledge show similar or different patterns across the four different samples?
(4) To what degree is the pattern of low representational competence but high conceptual knowledge, but not vice versa, visible in all four samples?
(5) Do gender, topic-specific learning opportunities, and individual preferences for specific learning content (as reflected in the choice of study program) explain differences and similarities between the four samples?


## RQ3 Latent Profile Analysis

```{r RQ3.LPA}

LPARQ3 <- '

[[init]]
iterators = c s;
c = 1:7;
s = 1:4;

filename = "RQ3_LPA_[[c]]profiles_sample[[s]].inp";
outputDirectory = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ3_LPA/sample[[s]]/";

[[/init]]

TITLE:
CESAR03_RQ3_LPA_[[c]]profiles_sample[[s]]

DATA:
FILE IS
"C:/local user data/CESAR0.3/Analysis_R/CESAR03.dat";

VARIABLE:

NAMES =
ID
Repko
Konzept
sample
male
leit_exp
teacher
MINT
;

USEVARIABLES ARE
repko konzept
;

useobservations are sample == [[s]];

[[c > 1]]

[[s < 3]]

AUXILIARY = ID
male (DCAT)
leit_exp (DCAT)
teacher (DCAT)
MINT (DCAT)
;

[[/s < 3]]

[[s > 2]]
!not teacher because no variation
AUXILIARY = ID
male (DCAT)
leit_exp (DCAT)
MINT (DCAT)
;

[[/s > 2]]



[[/c > 1]]

CLASSES = c([[c]]);

MISSING = all(9999);

ANALYSIS:

TYPE = mixture;
STARTS 1000 400;
PROCESS = 4 1;

MODEL:

%c#1%
[repko*] (m1);
[konzept*] (m2);
repko* (v1);
konzept* (v2);

[[c > 1]]

%c#2%
[repko*] (m3);
[konzept*] (m4);
repko* (v3);
konzept* (v4);

[[/c > 1]]

[[c > 2]]

%c#3%
[repko*] (m5);
[konzept*] (m6);
repko* (v5);
konzept* (v6);

[[/c > 2]]

[[c > 3]]

%c#4%
[repko*] (m7);
[konzept*] (m8);
repko* (v7);
konzept* (v8);

[[/c > 3]]

[[c > 4]]

%c#5%
[repko*] (m9);
[konzept*] (m10);
repko* (v9);
konzept* (v10);

[[/c > 4]]

[[c > 5]]

%c#6%
[repko*] (m11);
[konzept*] (m12);
repko* (v11);
konzept* (v12);

[[/c > 5]]

[[c > 6]]

%c#7%
[repko*] (m13);
[konzept*] (m14);
repko* (v13);
konzept* (v14);

[[/c > 6]]

OUTPUT: sampstat residual tech1 tech11 tech14;

plot:
type is plot1 plot2 plot3;
series is repko (1) konzept (2);

'

```

###Run analyses of created models 

```{r run.dataanalyses}

#Write template into textfile
write(LPARQ3, file = "LPA_RQ3.txt")

#Write Mplus input files based on template for all 30 combinations of N, E, missingdata(attrition).
createModels("LPA_RQ3.txt")

#Run Mplus input files
runModels(target = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ3_LPA/sample4", recursive = TRUE)

```

### Inspect results

```{r LPA.results}

RQ3_LPAs_outputs <- readModels(target = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ3_LPA/", what = c("summaries", "parameters", "class_counts", "lcCondMeans"), recursive = TRUE)

# Create a data frame with each model's summaries
all_fit_stats <- map_df(RQ3_LPAs_outputs, ~ .x$summaries, .id = "model_sample")

# Assuming you might want to split model_sample into separate 'model' and 'sample' columns
all_fit_stats <- all_fit_stats %>%
  mutate(model = sub("_.*", "", model_sample), # Adjust regex according to your naming convention
         Sample = sub(".*_", "", model_sample)) %>%
  select(Observations, Parameters:AICC, Entropy, T11_VLMR_PValue, BLRT_PValue, Sample, -LLCorrectionFactor) %>%
  mutate(Profiles = rep(c(1:7), 4)) %>%
  mutate(
    AIC = 2 * Parameters - 2 * LL,
    BIC = log(Observations) * Parameters - 2 * LL,
    aBIC = log((Observations + 2) / 24) * Parameters - 2 * LL,
    AIC3 = 3 * Parameters - 2 * LL,
    CAIC = log(Observations) * Parameters - 2 * LL + Parameters,
    AICC = AIC + (2 * Parameters^2 + 2 * Parameters) / (Observations - Parameters - 1)
  )

# Convert the data frame to long format
all_fit_stats_long <- pivot_longer(all_fit_stats,
                                   cols = -c(Profiles, Sample, Observations, Parameters),
                                   names_to = "statistic", 
                                   values_to = "value")

# View the resulting long format data frame
print(all_fit_stats_long)

all_fit_stats_long %>%
  filter(statistic == "AIC" | statistic == "BIC" | statistic == "AIC3" | statistic == "BIC" | statistic == "aBIC" | statistic == "CAIC") %>%
  mutate(Sample = fct_recode(factor(Sample),
                             "Teacher Education SU" = "sample1.out",
                             "Engineering TUK" = "sample2.out",
                             "Environmental Science ETH" = "sample3.out",
                             "Physics ETH" = "sample4.out")) %>%
  ggplot(aes(x = Profiles, y = value, group = statistic, shape = statistic, color = statistic)) +
  geom_line() +
  geom_point() +
  facet_wrap(~ Sample, scales = "free") +
  theme_bw() +
  scale_color_manual(values = palette())

ggsave("RQ3_Fit.png", width = 6, height = 4, dpi = 450)

# Create a data frame with each model's summaries
map_df(RQ3_LPAs_outputs, ~ .x$parameters$unstandardized, .id = "model_sample") %>%
  filter(paramHeader == "Means") %>%
  filter(param == "KONZEPT" | param == "REPKO") %>%
  mutate(Sample = sub(".*_", "", model_sample)) %>%
 mutate(param = fct_recode(param,
                            "Representational\nCompetence" = "REPKO",
                            "Conceptual\nKnowledge" = "KONZEPT")) %>%
  mutate(Sample = fct_recode(factor(Sample),
                             "Teacher Education SU" = "sample1.out",
                             "Engineering TUK" = "sample2.out",
                             "Environmental Science ETH" = "sample3.out",
                             "Physics ETH" = "sample4.out")) %>%
  filter(str_detect(model_sample, "3profiles")) %>%
  mutate(param = fct_relevel(param,
                             c("REPKO", "KONZEPT"))) %>%
  ggplot(aes(x = param, y = est, group = LatentClass)) +
  geom_line(position = position_dodge(width = 0.05)) +
  geom_point(position = position_dodge(width = 0.05)) +
  geom_errorbar(aes(ymin = est -1.68*se, ymax = est + 1.68*se), width = 0.1,
                position = position_dodge(width = 0.05)) +
  facet_wrap(~ Sample) +
  theme_bw() +
  scale_color_manual(values = palette()) +
  xlab("") +
  scale_y_continuous(limits = c(0, 12),
                     breaks = seq(0, 12, 2)) +
  ylab("Estimate +- 90% CI") +
  theme(legend.position = "none")


ggsave("RQ3_Profiles.png", width = 6, height = 4, dpi = 450)
# 
# #Profile sizes
# map_df(RQ3_LPAs_outputs, ~ .x$parameters$unstandardized, .id = "model_sample") %>%
#   filter(str_detect(model_sample, "3profiles")) %>%
#   filter(param == "C#1" |param == "C#2") %>%
#   mutate(Sample = sub(".*_", "", model_sample)) %>%
#   mutate(Sample = fct_recode(factor(Sample),
#                              "Teacher Education SU" = "sample1.out",
#                              "Engineering TUK" = "sample2.out",
#                              "Environmental Science ETH" = "sample3.out",
#                              "Physics ETH" = "sample4.out")) %>%
#   select(est, param, Sample) %>%
#   mutate(est = plogis(est)) %>%
#   pivot_wider(values_from = c("est"), names_from = "param") %>%
#   mutate(`C#3` = 1 - `C#1` - `C#2`) %>%
#   pivot_longer(c(`C#1`, `C#2`, `C#3`))
#   
# map_df(RQ3_LPAs_outputs, ~ .x$class_counts)

```




```{r RQ3.LPA.MG}

LPARQ3_MG <- '

[[init]]
iterators = c;
c = 1:7;

filename = "RQ3_LPA_Multigroup_[[c]]profiles.inp";
outputDirectory = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ3_LPA_Multigroup/";

[[/init]]

TITLE:
CESAR03_RQ3_LPA_Multigroup_[[c]]profiles

DATA:
FILE IS
"C:/local user data/CESAR0.3/Analysis_R/CESAR03.dat";

VARIABLE:

NAMES =
ID
Repko
Konzept
sample
male
leit_exp
teacher
MINT
;

USEVARIABLES ARE
repko konzept
;

CLASSES = s(4) c([[c]]);
knownclass = s(sample = 1 sample = 2 sample = 3 sample = 4);

MISSING = all(9999);

ANALYSIS:

TYPE = mixture;
STARTS 1000 400;
PROCESS = 4 1;

MODEL:

%OVERALL%

C ON S;

%s#1.c#1%

[repko*] (s1m1);
[konzept*] (s1m2);
repko* (s1v1);
konzept* (s1v2);

%s#2.c#1%

[repko*] (s2m1);
[konzept*] (s2m2);
repko* (s2v1);
konzept* (s2v2);

%s#3.c#1%

[repko*] (s3m1);
[konzept*] (s3m2);
repko* (s3v1);
konzept* (s3v2);

%s#4.c#1%

[repko*] (s4m1);
[konzept*] (s4m2);
repko* (s4v1);
konzept* (s4v2);

[[c > 1]]

%s#1.c#2%

[repko*] (s1m3);
[konzept*] (s1m4);
repko* (s1v3);
konzept* (s1v4);

%s#2.c#2%

[repko*] (s2m3);
[konzept*] (s2m4);
repko* (s2v3);
konzept* (s2v4);

%s#3.c#2%

[repko*] (s3m3);
[konzept*] (s3m4);
repko* (s3v3);
konzept* (s3v4);

%s#4.c#2%

[repko*] (s4m3);
[konzept*] (s4m4);
repko* (s4v3);
konzept* (s4v4);

[[/c > 1]]

[[c > 2]]

%s#1.c#3%

[repko*] (s1m5);
[konzept*] (s1m6);
repko* (s1v5);
konzept* (s1v6);

%s#2.c#3%

[repko*] (s2m5);
[konzept*] (s2m6);
repko* (s2v5);
konzept* (s2v6);

%s#3.c#3%

[repko*] (s3m5);
[konzept*] (s3m6);
repko* (s3v5);
konzept* (s3v6);

%s#4.c#3%

[repko*] (s6m5);
[konzept*] (s6m6);
repko* (s6v5);
konzept* (s6v6);

[[/c > 2]]

[[c > 3]]

%s#1.c#4%

[repko*] (s1m7);
[konzept*] (s1m8);
repko* (s1v7);
konzept* (s1v8);

%s#2.c#4%

[repko*] (s2m7);
[konzept*] (s2m8);
repko* (s2v7);
konzept* (s2v8);

%s#3.c#4%

[repko*] (s3m7);
[konzept*] (s3m8);
repko* (s3v7);
konzept* (s3v8);

%s#4.c#4%

[repko*] (s6m7);
[konzept*] (s6m8);
repko* (s6v7);
konzept* (s6v8);

[[/c > 3]]

[[c > 4]]

%s#1.c#5%

[repko*] (s1m9);
[konzept*] (s1m10);
repko* (s1v9);
konzept* (s1v10);

%s#2.c#5%

[repko*] (s2m9);
[konzept*] (s2m10);
repko* (s2v9);
konzept* (s2v10);

%s#3.c#5%

[repko*] (s3m9);
[konzept*] (s3m10);
repko* (s3v9);
konzept* (s3v10);

%s#4.c#5%

[repko*] (s6m9);
[konzept*] (s6m10);
repko* (s6v9);
konzept* (s6v10);

[[/c > 4]]

[[c > 5]]

%s#1.c#6%

[repko*] (s1m11);
[konzept*] (s1m12);
repko* (s1v11);
konzept* (s1v12);

%s#2.c#6%

[repko*] (s2m11);
[konzept*] (s2m12);
repko* (s2v11);
konzept* (s2v12);

%s#3.c#6%

[repko*] (s3m11);
[konzept*] (s3m12);
repko* (s3v11);
konzept* (s3v12);

%s#4.c#6%

[repko*] (s6m11);
[konzept*] (s6m12);
repko* (s6v11);
konzept* (s6v12);


[[/c > 5]]

[[c > 6]]

%s#1.c#7%

[repko*] (s1m13);
[konzept*] (s1m14);
repko* (s1v13);
konzept* (s1v14);

%s#2.c#7%

[repko*] (s2m13);
[konzept*] (s2m14);
repko* (s2v13);
konzept* (s2v14);

%s#3.c#7%

[repko*] (s3m13);
[konzept*] (s3m14);
repko* (s3v13);
konzept* (s3v14);

%s#4.c#7%

[repko*] (s6m13);
[konzept*] (s6m14);
repko* (s6v13);
konzept* (s6v14);

[[/c > 6]]

OUTPUT: sampstat residual tech1;

plot:
type is plot1 plot2 plot3;
series is repko (1) konzept (2);

'

```

### RQ3 LPA MG: Run analyses of created models MG

```{r run.dataanalyses.MG}

#Write template into textfile
write(LPARQ3_MG, file = "LPA_RQ3_MG.txt")

#Write Mplus input files based on template for all 30 combinations of N, E, missingdata(attrition).
createModels("LPA_RQ3_MG.txt")

#Run Mplus input files
runModels(target = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ3_LPA_Multigroup/", recursive = TRUE)

```

### RQ3 LPA MG: Inspect results

```{r LPA.results.MG}

RQ3_LPAs_MG_3output <- readModels(target = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ3_LPA_Multigroup/rq3_lpa_multigroup_3profiles.out", what = c("summaries", "parameters", "class_counts", "lcCondMeans"))
RQ3_LPAs_MG_3output #Fit indices

# Create a data frame with each model's summaries
RQ3_LPAs_MG_3output$parameters$unstandardized %>%
  filter(paramHeader == "Means") %>%
  filter(param == "KONZEPT" | param == "REPKO") %>%
  mutate(param = fct_relevel(param,
                             c("REPKO", "KONZEPT"))) %>%
 mutate(param = fct_recode(param,
                            "Representational Competence" = "REPKO",
                            "Conceptual Knowledge" = "KONZEPT")) %>%
  mutate(Sample = substr(LatentClass, 1, 1),
         Profile = substr(LatentClass, 3, 3)) %>%
    mutate(Sample = fct_recode(factor(Sample),
                             "Teacher Education SU" = "1",
                             "Engineering TUK" = "2",
                             "Environmental Science ETH" = "3",
                             "Physics ETH" = "4")) %>%
  ggplot(aes(x = param, y = est, group = LatentClass, color = Sample, shape = Profile)) +
  geom_line(position = position_dodge(width = 0.05), size = 1) +
  geom_point(position = position_dodge(width = 0.05), size = 2) +
  geom_errorbar(aes(ymin = est - 1.68*se, ymax = est + 1.68*se), width = 0.1,
                position = position_dodge(width = 0.05)) +
  theme_bw() +
  scale_color_manual(values = palette()) +
  xlab("") +
  ylab("Estimate +- 90% CI")

ggsave("RQ3_MG_Profiles.png", width = 7, height = 4, dpi = 450)
  
```


```{r RQ3.LPA.MG_STEP2}

LPA_RQ3_MG_STEP2 <- '


TITLE:
CESAR03_RQ3_LPA_Multigroup_3profiles_STEP2;

DATA:
FILE IS
"C:/local user data/CESAR0.3/Analysis_R/CESAR03.dat";

VARIABLE:

NAMES =
ID
Repko
Konzept
sample
male
leit_exp
teacher
MINT
;

USEVARIABLES ARE
repko konzept
;

CLASSES = s(4) c(3);
knownclass = s(sample = 1 sample = 2 sample = 3 sample = 4);

MISSING = all(9999);

ANALYSIS:

TYPE = mixture;
STARTS 1000 400;
PROCESS = 4 1;

MODEL:

%OVERALL%

C ON S;

%s#1.c#1%

[repko*] (s1m1);
[konzept*] (s1m2);
repko* (s1v1);
konzept* (s1v2);

%s#2.c#1%

[repko*] (s1m1);
[konzept*] (s1m2);
repko* (s1v1);
konzept* (s1v2);

%s#3.c#1%

[repko*] (s3m1);
[konzept*] (s3m2);
repko* (s3v1);
konzept* (s3v2);

%s#4.c#1%

[repko*] (s4m1);
[konzept*] (s4m2);
repko* (s4v1);
konzept* (s4v2);

%s#1.c#2%

[repko*] (s1m3);
[konzept*] (s1m4);
repko* (s1v3);
konzept* (s1v4);

%s#2.c#2%

[repko*] (s2m3);
[konzept*] (s2m4);
repko* (s2v3);
konzept* (s2v4);

%s#3.c#2%

[repko*] (s1m3);
[konzept*] (s1m4);
repko* (s1v3);
konzept* (s1v4);

%s#4.c#2%

[repko*] (s4m3);
[konzept*] (s4m4);
repko* (s4v3);
konzept* (s4v4);

%s#1.c#3%

[repko*] (s1m5);
[konzept*] (s1m6);
repko* (s1v5);
konzept* (s1v6);

%s#2.c#3%

[repko*] (s2m5);
[konzept*] (s2m6);
repko* (s2v5);
konzept* (s2v6);

%s#3.c#3%

[repko*] (s3m5);
[konzept*] (s3m6);
repko* (s3v5);
konzept* (s3v6);

%s#4.c#3%

[repko*] (s6m5);
[konzept*] (s6m6);
repko* (s6v5);
konzept* (s6v6);

OUTPUT: sampstat residual tech1;

plot:
type is plot1 plot2 plot3;
series is repko (1) konzept (2);

'

```

### RQ3 LPA MG: Run analyses of created models MG

```{r run.dataanalyses.MG}
#dir.create("CESAR03_RQ3_LPA_Multigroup_STEP2")

writeLines(LPA_RQ3_MG_STEP2, "CESAR03_RQ3_LPA_Multigroup_STEP2/LPA_RQ3_MG_STEP2.inp")

#Run Mplus input files
runModels(target = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ3_LPA_Multigroup_STEP2/", recursive = TRUE)

```

### RQ3 LPA MG: Inspect results

```{r LPA.results.MG}

RQ3_LPAs_MG_STEP2_outputs <- readModels(target = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ3_LPA_Multigroup_STEP2/", what = c("summaries", "parameters", "class_counts", "lcCondMeans"), recursive = TRUE)

# CESAR03_RQ3_LPA_Multigroup_3profiles Estimated using MLR 
# Number of obs: 515, number of (free) parameters: 59 
# AIC = 5963.944, BIC = 6214.35

RQ3_LPAs_MG_3output$summaries$Observations
RQ3_LPAs_MG_3output$summaries$Parameters
RQ3_LPAs_MG_3output$summaries$LL
RQ3_LPAs_MG_3output$summaries$LLCorrectionFactor

RQ3_LPAs_MG_STEP2_outputs$summaries$Observations
RQ3_LPAs_MG_STEP2_outputs$summaries$Parameters
RQ3_LPAs_MG_STEP2_outputs$summaries$LL
RQ3_LPAs_MG_STEP2_outputs$summaries$LLCorrectionFactor



# Difference Testing Using the Loglikelihood
# 
# Following are the steps needed to compute a chi-square difference test based on loglikelihood values and scaling correction factors obtained with the MLR estimator.
# 
# Estimate the nested and comparison models using MLR. The printout gives loglikelihood values L0 and L1 for the H0 and H1 models, respectively, as well as scaling correction factors c0 and c1 for the H0 and H1 models, respectively. For example,
L1 = -2922.972
c1 = 0.9399
p1 = 59

L0 = -2925.366
c0 = 0.9022
p0 = 51

cd = (p0 * c0 - p1*c1)/(p0 - p1) #1.180237
TRd = -2*(L0 - L1)/cd #4.056811
pchisq(4.056811, df = 8, lower.tail = FALSE) #p = .852


# Estimated using MLR 
# Number of obs: 515, number of (free) parameters: 51
# AIC = 5952.731, BIC = 6169.184 

RQ3_LPAs_MG_STEP2_outputs$parameters$unstandardized %>%
  filter(paramHeader == "Means") %>%
  filter(param == "KONZEPT" | param == "REPKO") %>%
  mutate(param = fct_relevel(param,
                             c("REPKO", "KONZEPT"))) %>%
  mutate(param = fct_recode(param,
                            "Representational Competence" = "REPKO",
                            "Conceptual Knowledge" = "KONZEPT")) %>%
  mutate(Sample = substr(LatentClass, 1, 1),
         Profile = substr(LatentClass, 3, 3)) %>%
    mutate(Sample = fct_recode(factor(Sample),
                             "Teacher Education SU" = "1",
                             "Engineering TUK" = "2",
                             "Environmental Science ETH" = "3",
                             "Physics ETH" = "4")) %>%
  ggplot(aes(x = param, y = est, group = LatentClass, color = Sample, shape = Profile)) +
  geom_line(position = position_dodge(width = 0.05), size = 1) +
  geom_point(position = position_dodge(width = 0.05), size = 2) +
  geom_errorbar(aes(ymin = est - 1.68*se, ymax = est + 1.68*se), width = 0.1,
                position = position_dodge(width = 0.05)) +
  theme_bw() +
  scale_color_manual(values = palette()) +
  xlab("") +
  ylab("Estimate +- 90% CI")

ggsave("RQ3_MG_STEP2_Profiles.png", width = 7, height = 4, dpi = 450)
  
  
```

```{r RQ3.LPA.MG_STEP3}

LPA_RQ3_MG_STEP3 <- '


TITLE:
CESAR03_RQ3_LPA_Multigroup_3profiles_STEP3;

DATA:
FILE IS
"C:/local user data/CESAR0.3/Analysis_R/CESAR03.dat";

VARIABLE:

NAMES =
ID
Repko
Konzept
sample
male
leit_exp
teacher
MINT
;

USEVARIABLES ARE
repko konzept
;

CLASSES = s(4) c(3);
knownclass = s(sample = 1 sample = 2 sample = 3 sample = 4);

MISSING = all(9999);

ANALYSIS:

TYPE = mixture;
STARTS 1000 400;
PROCESS = 4 1;

MODEL:

%OVERALL%

C ON S;

%s#1.c#1%

[repko*] (m1);
[konzept*] (m2);
repko* (v1);
konzept* (v2);

%s#2.c#1%

[repko*] (m1);
[konzept*] (m2);
repko* (v1);
konzept* (v2);

%s#1.c#2%

[repko*] (m3);
[konzept*] (m4);
repko* (v3);
konzept* (v4);

%s#2.c#2%

[repko*] (m3);
[konzept*] (m4);
repko* (v3);
konzept* (v4);

%s#1.c#3%

[repko*] (m5);
[konzept*] (m6);
repko* (v5);
konzept* (v6);

%s#3.c#1%

[repko*] (m5);
[konzept*] (m6);
repko* (v5);
konzept* (v6);



%s#2.c#3%

[repko*] (m7);
[konzept*] (m8);
repko* (v7);
konzept* (s2v8);

%s#4.c#1%

[repko*] (m7);
[konzept*] (m8);
repko* (v7);
konzept* (s2v8);


%s#3.c#2%

[repko*] (m9);
[konzept*] (m10);
repko* (v9);
konzept* (v10);

%s#3.c#3%

[repko*] (m11);
[konzept*] (m12);
repko* (v11);
konzept* (v12);


%s#4.c#2%

[repko*] (m13);
[konzept*] (m14);
repko* (v13);
konzept* (v14);

%s#4.c#3%

[repko*] (m15);
[konzept*] (m16);
repko* (v15);
konzept* (v16);

OUTPUT: sampstat residual tech1;

plot:
type is plot1 plot2 plot3;
series is repko (1) konzept (2);

'

```

### RQ3 LPA MG STEP3: Run analyses of created models MG

```{r run.dataanalyses.MG}
dir.create("CESAR03_RQ3_LPA_Multigroup_STEP3")

writeLines(LPA_RQ3_MG_STEP3, "CESAR03_RQ3_LPA_Multigroup_STEP3/LPA_RQ3_MG_STEP3.inp")

#Run Mplus input files
runModels(target = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ3_LPA_Multigroup_STEP3/", recursive = TRUE)

```

### RQ3 LPA MG STEP3: Inspect results

```{r LPA.results.MG.STEP3}

RQ3_LPAs_MG_STEP3_outputs <- readModels(target = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ3_LPA_Multigroup_STEP3/", what = c("summaries", "parameters", "class_counts", "lcCondMeans"), recursive = TRUE)

# Difference Testing Using the Loglikelihood
# 
# Following are the steps needed to compute a chi-square difference test based on loglikelihood values and scaling correction factors obtained with the MLR estimator.
# 
# Estimate the nested and comparison models using MLR. The printout gives loglikelihood values L0 and L1 for the H0 and H1 models, respectively, as well as scaling correction factors c0 and c1 for the H0 and H1 models, respectively. For example,


L1 = RQ3_LPAs_MG_outputs$summaries$LL
c1 = RQ3_LPAs_MG_outputs$summaries$LLCorrectionFactor
p1 = RQ3_LPAs_MG_outputs$summaries$Parameters

L1 = RQ3_LPAs_MG_STEP2_outputs$summaries$LL
c1 = RQ3_LPAs_MG_STEP2_outputs$summaries$LLCorrectionFactor
p1 = RQ3_LPAs_MG_STEP2_outputs$summaries$Parameters

L0 = RQ3_LPAs_MG_STEP3_outputs$summaries$LL
c0 = RQ3_LPAs_MG_STEP3_outputs$summaries$LLCorrectionFactor
p0 = RQ3_LPAs_MG_STEP3_outputs$summaries$Parameters

cd = (p0 * c0 - p1*c1)/(p0 - p1) #1.180237
TRd = -2*(L0 - L1)/cd #4.056811
pchisq(TRd, df = 8, lower.tail = FALSE) #p = .156 for step 3 - step 2 (8 df), .751 for step 3 - step 1
pchisq(TRd, df = 16, lower.tail = FALSE) #p = .156 for step 3 - step 2, .751 for step 3 - step 1 (16 df)

# Estimated using MLR 
# Number of obs: 515, number of (free) parameters: 51
# AIC = 5952.731, BIC = 6169.184 

RQ3_LPAs_MG_STEP3_outputs$class_counts$modelEstimated.patterns$proportion
RQ3_LPAs_MG_STEP3_outputs$parameters$unstandardized %>%
  filter(paramHeader == "Means") %>%
  filter(param == "KONZEPT" | param == "REPKO") %>%
  mutate(param = fct_relevel(param,
                             c("REPKO", "KONZEPT"))) %>%
  mutate(param = fct_recode(param,
                            "Representational Competence" = "REPKO",
                            "Conceptual Knowledge" = "KONZEPT")) %>%
  mutate(Sample = substr(LatentClass, 1, 1),
         Profile = substr(LatentClass, 3, 3)) %>%
    mutate(Sample = fct_recode(factor(Sample),
                             "Teacher Education SU" = "1",
                             "Engineering TUK" = "2",
                             "Environmental Science ETH" = "3",
                             "Physics ETH" = "4")) %>%
  #(21% / 10% / 7% / 10%)
#    variable class    count proportion
# 1        S     1 188.0000    0.36505
# 2        S     2 149.0000    0.28932
# 3        S     3  98.0000    0.19029
# 4        S     4  80.0000    0.15534
# 5        C     1 245.8263    0.47733
# 6        C     2 123.0780    0.23899
# 7        C     3 146.0957    0.28368
#   > RQ3_LPAs_MG_STEP3_outputs$class_counts$modelEstimated.patterns$count
#  [1] 109.78184  66.60080  11.61735
#  [4]  49.49098  33.81425  65.69477
#  [7]  37.46231   7.40207  53.13561
# [10]  49.09115  15.26090  15.64794
# data.frame(Sample = c(rep(1, 3),
#                       rep(2, 3),
#                       rep(3, 3),
#                       rep(4, 3)),
#            Profile = rep(1:3, 4),
#            N = c(rep(188, 3),
#                  rep(149, 3),
#                  rep(98, 3),
#                  rep(80, 3)),
#            n_Profile = RQ3_LPAs_MG_STEP3_outputs$class_counts$modelEstimated.patterns$count) %>%
#   mutate(Profile_prop = n_Profile/N)
  mutate(Profile_label = fct_recode(LatentClass,
                                    "RC low / CK very low\n(58% / 33% / 0% / 19%)" = "1.1",
                                    "RC low / CK low\n(35% / 23% / 8% / 0%)" = "1.2",
                                    "RC very high / CK low\n(6% / 0% / 0% / 0%)" = "1.3",
                                    "RC low / CK very low\n(58% / 33% / 0% / 19%)" = "2.1",
                                    "RC low / CK low\n(35% / 23% / 8% / 0%)" = "2.2",
                                    "RC high / CK high\n(0% / 44% / 0% / 61%)" = "2.3",
                                    "RC high / CK low\n(0% / 0% / 38% / 0%)" = "3.1",
                                    "RC low / CK low\n(35% / 23% / 8% / 0%)" = "3.2",
                                    "RC high / CK very low\n(0% / 0% / 54% / 0%)" = "3.3",
                                    "RC high / CK high\n(0% / 44% / 0% / 61%)" = "4.1",
                                    "RC low / CK very low\n(58% / 33% / 0% / 19%)" = "4.2",
                                    "RC very high / CK very high\n(0% / 0% / 0% / 20%)" = "4.3"
                                    )) %>%
  mutate(Profile_label = fct_relevel(Profile_label,
                                     c("RC low / CK very low\n(58% / 33% / 0% / 19%)",
                                       "RC low / CK low\n(35% / 23% / 8% / 0%)",
                                       "RC high / CK very low\n(0% / 0% / 54% / 0%)",
                                       "RC high / CK low\n(0% / 0% / 38% / 0%)",
                                       "RC high / CK high\n(0% / 44% / 0% / 61%)",
                                       "RC very high / CK low\n(6% / 0% / 0% / 0%)",
                                       "RC very high / CK very high\n(0% / 0% / 0% / 20%)"))) %>%
  mutate(Profile_label_RC  = ifelse(str_detect(Profile_label, "RC low"), "Low", ifelse(str_detect(Profile_label, "RC high"), "High", "Very high")),
         Profile_label_CK  = ifelse(str_detect(Profile_label, "CK very low"), "Very low", ifelse(str_detect(Profile_label, "CK low"), "Low", ifelse(str_detect(Profile_label, "CK high"), "High", "Very high")))) %>%
  ggplot(aes(x = param, y = est, group = interaction(Profile_label_RC, Profile_label_CK, Sample), linetype = Profile_label, shape = Profile_label)) +
  geom_line(position = position_dodge(width = 0.1), size = 1) +
  geom_point(position = position_dodge(width = 0.1), size = 2) +
  geom_errorbar(aes(ymin = est - 1.68*se, ymax = est + 1.68*se), width = 0.1,
                position = position_dodge(width = 0.1)) +
  theme_bw() +
  scale_color_manual(values = palette()) +
  xlab("") +
  ylab("Estimate +- 90% CI") +
  scale_y_continuous(limits = c(0, 12),
                     breaks = c(0:12),
                     sec.axis = sec_axis( trans=~., name="",
                     breaks = c(0:12))) +
  geom_hline(aes(yintercept = 3), color = "grey", linetype = 2, size = 1.1) +
  geom_hline(aes(yintercept = 6), color = "grey", linetype = 2, size = 1.1) +
  geom_hline(aes(yintercept = 9), color = "grey", linetype = 2, size = 1.1) +
  guides(linetype = guide_legend(title = "Profile\n(% in samples)"),
         shape = guide_legend(title = "Profile\n(% in samples)"),
         color = guide_legend(title = "Profile\n(% in samples)")) +
  scale_linetype_manual(values = c(1, 1, 2, 2, 2, 3, 3)) +
  scale_shape_manual(values = c(21, 22, 21, 22, 23, 22, 24)) +
  theme(panel.grid.minor = element_blank()) +
  theme(panel.grid.major = element_blank()) +
  theme(legend.key.size = unit(1, "cm"))
  

ggsave("RQ3_MG_STEP3_Profiles_labels.png", width = 7, height = 4, dpi = 450)

#Figure with profile labels


```

## RQ5 LPA MG DCAT

```{r RQ5.LPA.DCAT}

LPARQ5_DCAT <- '

[[init]]
iterators = s;
s = 1:4;

filename = "RQ5_LPA_[[c]]profiles_sample[[s]].inp";
outputDirectory = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ5_LPA_DCAT/sample[[s]]/";

[[/init]]

TITLE:
CESAR03_RQ5_LPA_3profiles_DCAT_sample[[s]]

DATA:
FILE IS
"C:/local user data/CESAR0.3/Analysis_R/CESAR03.dat";

VARIABLE:

NAMES =
ID
Repko
Konzept
sample
male
leit_exp
teacher
MINT
;

USEVARIABLES ARE
repko konzept
;

useobservations are sample == [[s]];

[[s < 3]]

AUXILIARY = ID
male (DCAT)
leit_exp (DCAT)
teacher (DCAT)
MINT (DCAT)
;

[[/s < 3]]

[[s > 2]]
!not teacher because no variation
AUXILIARY = ID
male (DCAT)
leit_exp (DCAT)
MINT (DCAT)
;

[[/s > 2]]

CLASSES = c(3);

MISSING = all(9999);

ANALYSIS:

TYPE = mixture;
STARTS 1000 400;
PROCESS = 4 1;

MODEL:

[[s == 1]]

%c#1%
[repko@4.118];
[konzept@1.049];
repko@3.167;
konzept@0.634;

%c#2%
[repko@4.914];
[konzept@3.336];
repko@3.866;
konzept@2.333;

%c#3%
[repko@9.667];
[konzept@5.274];
repko@2.055;
konzept@5.723;

[[/s == 1]]

[[s == 2]]

%c#1%
[repko@4.118];
[konzept@1.049];
repko@3.167;
konzept@0.634;

%c#2%
[repko@4.914];
[konzept@3.336];
repko@3.866;
konzept@2.333;

%c#3%
[repko@8.617];
[konzept@6.900];
repko@3.640;
konzept@8.035;

[[/s == 2]]

[[s == 3]]

%c#1%
[repko@9.667];
[konzept@5.274];
repko@2.055;
konzept@5.723;

%c#2%
[repko@4.950];
[konzept@4.444];
repko@0.593;
konzept@0.695;

%c#3%
[repko@7.108];
[konzept@1.162];
repko@5.203;
konzept@0.905;

[[/s == 3]]

[[s == 4]]

%c#1%
[repko@8.617];
[konzept@6.900];
repko@3.640;
konzept@8.035;

%c#2%
[repko@5.258];
[konzept@2.325;
repko@1.387;
konzept@1.349;

%c#3%
[repko@11.407];
[konzept@10.788];
repko@0.303;
konzept@1.422;

[[/s == 4]]

OUTPUT: sampstat residual tech1 tech11 tech14;

plot:
type is plot1 plot2 plot3;
series is repko (1) konzept (2);

'

```

###Run analyses of created models 

```{r run.dataanalyses}

#Write template into textfile
write(LPARQ5_DCAT, file = "LPA_RQ5_DCAT.txt")

#Write Mplus input files based on template for all 30 combinations of N, E, missingdata(attrition).
createModels("LPA_RQ5_DCAT.txt")

#Run Mplus input files
runModels(target = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ5_LPA_DCAT/", recursive = TRUE)

```

### Inspect results

```{r LPA.results}

RQ5_LPAs_DCAT_outputs <- readModels(target = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ5_LPA_DCAT/", what = c("summaries", "parameters", "class_counts", "lcCondMeans"), recursive = TRUE)

RQ5_lcCondMeans <-
rbind(
rbind(
RQ5_LPAs_DCAT_outputs[[1]]$lcCondMeans$MALE$parameters %>% mutate(variable = "male"),
RQ5_LPAs_DCAT_outputs[[1]]$lcCondMeans$MINT$parameters %>% mutate(variable = "MINT"),
RQ5_LPAs_DCAT_outputs[[1]]$lcCondMeans$TEACHER$parameters %>% mutate(variable = "Teacher"),
RQ5_LPAs_DCAT_outputs[[1]]$lcCondMeans$LEIT_EXP$parameters%>% mutate(variable = "Swing")) %>% mutate(Sample = "Teacher Education SU"),
rbind(
RQ5_LPAs_DCAT_outputs[[2]]$lcCondMeans$MALE$parameters %>% mutate(variable = "male"),
RQ5_LPAs_DCAT_outputs[[2]]$lcCondMeans$MINT$parameters %>% mutate(variable = "MINT"),
RQ5_LPAs_DCAT_outputs[[2]]$lcCondMeans$TEACHER$parameters %>% mutate(variable = "Teacher"),
RQ5_LPAs_DCAT_outputs[[2]]$lcCondMeans$LEIT_EXP$parameters%>% mutate(variable = "Swing")) %>% mutate(Sample = "Engineering TUK"),
rbind(
RQ5_LPAs_DCAT_outputs[[3]]$lcCondMeans$MALE$parameters %>% mutate(variable = "male"),
RQ5_LPAs_DCAT_outputs[[3]]$lcCondMeans$MINT$parameters %>% mutate(variable = "MINT"),
RQ5_LPAs_DCAT_outputs[[3]]$lcCondMeans$LEIT_EXP$parameters%>% mutate(variable = "Swing")) %>% mutate(Sample = "Environmental Science ETH"),
rbind(
RQ5_LPAs_DCAT_outputs[[4]]$lcCondMeans$MALE$parameters %>% mutate(variable = "male"),
RQ5_LPAs_DCAT_outputs[[4]]$lcCondMeans$MINT$parameters %>% mutate(variable = "MINT"),
RQ5_LPAs_DCAT_outputs[[4]]$lcCondMeans$LEIT_EXP$parameters%>% mutate(variable = "Swing")) %>% mutate(Sample = "Physics ETH")
) %>% mutate(across(
    .cols = -any_of(c("variable", "Sample")),
    .fns = ~ if (is.character(.)) as.numeric(.) else .
  )) %>%
  dplyr::rename("Profile" = "class")

str(RQ5_lcCondMeans)

#x-Axis: Profile; group: Sample; first:
#name profiles according to above:
  # mutate(Profile_label = fct_recode(LatentClass,
  #                                   "RC low / CK very low\n(58% / 33% / 0% / 19%)" = "1.1",
  #                                   "RC low / CK low\n(35% / 23% / 8% / 0%)" = "1.2",
  #                                   "RC very high / CK low\n(6% / 0% / 0% / 0%)" = "1.3",
  #                                   "RC low / CK very low\n(58% / 33% / 0% / 19%)" = "2.1",
  #                                   "RC low / CK low\n(35% / 23% / 8% / 0%)" = "2.2",
  #                                   "RC high / CK high\n(0% / 44% / 0% / 61%)" = "2.3",
  #                                   "RC high / CK low\n(0% / 0% / 38% / 0%)" = "3.1",
  #                                   "RC low / CK low\n(35% / 23% / 8% / 0%)" = "3.2",
  #                                   "RC high / CK very low\n(0% / 0% / 54% / 0%)" = "3.3",
  #                                   "RC high / CK high\n(0% / 44% / 0% / 61%)" = "4.1",
  #                                   "RC low / CK very low\n(58% / 33% / 0% / 19%)" = "4.2",
  #                                   "RC very high / CK very high\n(0% / 0% / 0% / 20%)" = "4.3"
  #                                   )) %>%
  # mutate(Profile_label = fct_relevel(Profile_label,
  #                                    c("RC low / CK very low\n(58% / 33% / 0% / 19%)",
  #                                      "RC low / CK low\n(35% / 23% / 8% / 0%)",
  #                                      "RC high / CK very low\n(0% / 0% / 54% / 0%)",
  #                                      "RC high / CK low\n(0% / 0% / 38% / 0%)",
  #                                      "RC high / CK high\n(0% / 44% / 0% / 61%)",
  #                                      "RC very high / CK low\n(6% / 0% / 0% / 0%)",
  #                                      "RC very high / CK very high\n(0% / 0% / 0% / 20%)"))) %>%
  # mutate(Profile_label_RC  = ifelse(str_detect(Profile_label, "RC low"), "Low", ifelse(str_detect(Profile_label, "RC high"), "High", "Very high")),
  #        Profile_label_CK  = ifelse(str_detect(Profile_label, "CK very low"), "Very low", ifelse(str_detect(Profile_label, "CK low"), "Low", ifelse(str_detect(Profile_label, "CK high"), "High", "Very high")))) %>%


RQ5_lcCondMeans %>%
  filter(category == "2" & variable == "male") %>%
  mutate(Profile_label = c("RC low / CK very low\n(58% / 33% / 0% / 19%)",
                                    "RC low / CK low\n(35% / 23% / 8% / 0%)",
                                    "RC very high / CK low\n(6% / 0% / 0% / 0%)",
                                    "RC low / CK very low\n(58% / 33% / 0% / 19%)",
                                    "RC low / CK low\n(35% / 23% / 8% / 0%)",
                                    "RC high / CK high\n(0% / 44% / 0% / 61%)",
                                    "RC high / CK low\n(0% / 0% / 38% / 0%)",
                                    "RC low / CK low\n(35% / 23% / 8% / 0%)",
                                    "RC high / CK very low\n(0% / 0% / 54% / 0%)",
                                    "RC high / CK high\n(0% / 44% / 0% / 61%)",
                                    "RC low / CK very low\n(58% / 33% / 0% / 19%)",
                                    "RC very high / CK very high\n(0% / 0% / 0% / 20%)")) %>%
    mutate(Profile_label = fct_relevel(Profile_label,
                                     c("RC low / CK very low\n(58% / 33% / 0% / 19%)",
                                       "RC low / CK low\n(35% / 23% / 8% / 0%)",
                                       "RC high / CK very low\n(0% / 0% / 54% / 0%)",
                                       "RC high / CK low\n(0% / 0% / 38% / 0%)",
                                       "RC high / CK high\n(0% / 44% / 0% / 61%)",
                                       "RC very high / CK low\n(6% / 0% / 0% / 0%)",
                                       "RC very high / CK very high\n(0% / 0% / 0% / 20%)"))) %>%
  mutate(Sample = fct_relevel(Sample,
                              c("Teacher Education SU",
                                "Engineering TUK",
                                "Environmental Science ETH",
                                "Physics ETH"))) %>%
  ggplot(aes(x = factor(Profile_label), y = prob, group = Sample, shape = Sample, color = Sample)) +
    geom_point(size = 2.5, position = position_dodge(width = 0.2)) +
    geom_errorbar(aes(ymin = prob - 1.68*se, ymax = prob + 1.68*se),
                  width = 0.1, size = 1, position = position_dodge(width = 0.2)) +
    scale_y_continuous(name = "Estimated proportion\nof males (+- 90% CI)",
                       limits = c(-0.15, 1.15),
                       breaks = seq(0, 1, 0.2),
                       labels = seq(0, 1, 0.2),
                       sec.axis = sec_axis(~ ., 
                                           name = "",
                                           breaks = seq(0, 1, 0.2),
                                           labels = seq(0, 1, 0.2)
                                           )
                       ) +
    geom_hline(yintercept = 3, color = "grey", linetype = 2) +
    theme(panel.background = element_blank(),
          panel.border = element_rect(color = "black", fill = "NA"),
          axis.line = element_line(),
          axis.text = element_text(color = "black"),
          legend.position = "top",
          plot.title = element_text(hjust = 0.5, size = 12), # Centered and bold with a smaller font size
          plot.title.position = "plot", # Position the title over the plot area
          ) +
    scale_color_manual(values = palette(), name = "Sample") +
    labs(title = "", x = "Profile", y = "") +
    theme(plot.margin = margin(0, 0, 0, 0))

ggsave("RQ5_male.png", dpi = 450, width = 11, height = 4)



RQ5_lcCondMeans %>%
  filter(category == "2" & variable == "MINT") %>%
  mutate(Profile_label = c("RC low / CK very low\n(58% / 33% / 0% / 19%)",
                                    "RC low / CK low\n(35% / 23% / 8% / 0%)",
                                    "RC very high / CK low\n(6% / 0% / 0% / 0%)",
                                    "RC low / CK very low\n(58% / 33% / 0% / 19%)",
                                    "RC low / CK low\n(35% / 23% / 8% / 0%)",
                                    "RC high / CK high\n(0% / 44% / 0% / 61%)",
                                    "RC high / CK low\n(0% / 0% / 38% / 0%)",
                                    "RC low / CK low\n(35% / 23% / 8% / 0%)",
                                    "RC high / CK very low\n(0% / 0% / 54% / 0%)",
                                    "RC high / CK high\n(0% / 44% / 0% / 61%)",
                                    "RC low / CK very low\n(58% / 33% / 0% / 19%)",
                                    "RC very high / CK very high\n(0% / 0% / 0% / 20%)")) %>%
    mutate(Profile_label = fct_relevel(Profile_label,
                                     c("RC low / CK very low\n(58% / 33% / 0% / 19%)",
                                       "RC low / CK low\n(35% / 23% / 8% / 0%)",
                                       "RC high / CK very low\n(0% / 0% / 54% / 0%)",
                                       "RC high / CK low\n(0% / 0% / 38% / 0%)",
                                       "RC high / CK high\n(0% / 44% / 0% / 61%)",
                                       "RC very high / CK low\n(6% / 0% / 0% / 0%)",
                                       "RC very high / CK very high\n(0% / 0% / 0% / 20%)"))) %>%
  mutate(Sample = fct_relevel(Sample,
                              c("Teacher Education SU",
                                "Engineering TUK",
                                "Environmental Science ETH",
                                "Physics ETH"))) %>%
  ggplot(aes(x = factor(Profile_label), y = prob, group = Sample, shape = Sample, color = Sample)) +
    geom_point(size = 2.5, position = position_dodge(width = 0.2)) +
    geom_errorbar(aes(ymin = prob - 1.68*se, ymax = prob + 1.68*se),
                  width = 0.1, size = 1, position = position_dodge(width = 0.2)) +
    scale_y_continuous(name = "Estimated proportion\n of STEM students (+- 90% CI)",
                       limits = c(-0.15, 1.15),
                       breaks = seq(0, 1, 0.2),
                       labels = seq(0, 1, 0.2),
                       sec.axis = sec_axis(~ ., 
                                           name = "",
                                           breaks = seq(0, 1, 0.2),
                                           labels = seq(0, 1, 0.2)
                                           )
                       ) +
    geom_hline(yintercept = 3, color = "grey", linetype = 2) +
    theme(panel.background = element_blank(),
          panel.border = element_rect(color = "black", fill = "NA"),
          axis.line = element_line(),
          axis.text = element_text(color = "black"),
          legend.position = "top",
          plot.title = element_text(hjust = 0.5, size = 12), # Centered and bold with a smaller font size
          plot.title.position = "plot", # Position the title over the plot area
          ) +
    scale_color_manual(values = palette(), name = "Sample") +
    labs(title = "", x = "Profile", y = "") +
    theme(plot.margin = margin(0, 0, 0, 0))

ggsave("RQ5_STEM.png", dpi = 450, width = 11, height = 4)

RQ5_lcCondMeans %>%
  filter(category == "2" & variable == "Teacher" & Sample == "Teacher Education SU") %>%
  mutate(Profile_label = c("RC low / CK very low\n(58% / 33% / 0% / 19%)",
                                    "RC low / CK low\n(35% / 23% / 8% / 0%)",
                                    "RC very high / CK low\n(6% / 0% / 0% / 0%)")) %>%
    mutate(Profile_label = fct_relevel(Profile_label,
                                     c("RC low / CK very low\n(58% / 33% / 0% / 19%)",
                                       "RC low / CK low\n(35% / 23% / 8% / 0%)",
                                       "RC very high / CK low\n(6% / 0% / 0% / 0%)"))) %>%
  mutate(Sample = fct_relevel(Sample,
                              c("Teacher Education SU",
                                "Engineering TUK",
                                "Environmental Science ETH",
                                "Physics ETH"))) %>%
  ggplot(aes(x = factor(Profile_label), y = prob, group = Sample, shape = Sample, color = Sample)) +
    geom_point(size = 2.5, position = position_dodge(width = 0.2)) +
    geom_errorbar(aes(ymin = prob - 1.68*se, ymax = prob + 1.68*se),
                  width = 0.1, size = 1, position = position_dodge(width = 0.2)) +
    scale_y_continuous(name = "Estimated proportion\nof teacher students (+- 90% CI)",
                       limits = c(-0.15, 1.15),
                       breaks = seq(0, 1, 0.2),
                       labels = seq(0, 1, 0.2),
                       sec.axis = sec_axis(~ ., 
                                           name = "",
                                           breaks = seq(0, 1, 0.2),
                                           labels = seq(0, 1, 0.2)
                                           )
                       ) +
    geom_hline(yintercept = 3, color = "grey", linetype = 2) +
    theme(panel.background = element_blank(),
          panel.border = element_rect(color = "black", fill = "NA"),
          axis.line = element_line(),
          axis.text = element_text(color = "black"),
          legend.position = "top",
          plot.title = element_text(hjust = 0.5, size = 12), # Centered and bold with a smaller font size
          plot.title.position = "plot", # Position the title over the plot area
          ) +
    scale_color_manual(values = palette(), name = "Sample") +
    labs(title = "", x = "Profile", y = "") +
    theme(plot.margin = margin(0, 0, 0, 0))

ggsave("RQ5_Teacher.png", dpi = 450, width = 11, height = 4)


RQ5_lcCondMeans %>%
  filter(variable == "Swing") %>%
  mutate(Profile_label = c(rep("\nRC low / CK very low", 4),
                                    rep("RC low / CK low", 4),
                                    rep("RC very high / CK low", 4),
                                    rep("\nRC low / CK very low", 4),
                                    rep("RC low / CK low", 4),
                                    rep("\nRC high / CK high", 4),
                                    rep("RC high / CK low", 4),
                                    rep("RC low / CK low", 4),
                                    rep("\nRC high / CK very low", 4),
                                    rep("\nRC high / CK high", 4),
                                    rep("\nRC low / CK very low", 4),
                                    rep("\nRC very high / CK very high", 4))) %>%
    mutate(Profile_label = fct_relevel(Profile_label,
                                     c("\nRC low / CK very low",
                                       "RC low / CK low",
                                       "\nRC high / CK very low",
                                       "RC high / CK low",
                                       "\nRC high / CK high",
                                       "RC very high / CK low",
                                       "\nRC very high / CK very high"))) %>%
  mutate(Sample = fct_relevel(Sample,
                              c("Teacher Education SU",
                                "Engineering TUK",
                                "Environmental Science ETH",
                                "Physics ETH"))) %>%
  ggplot(aes(x = category, y = prob, group = Sample, shape = Sample, color = Sample)) +
    geom_point(size = 2.5, position = position_dodge(width = 0.2)) +
    geom_errorbar(aes(ymin = prob - 1.68*se, ymax = prob + 1.68*se),
                  width = 0.1, size = 1, position = position_dodge(width = 0.2)) +
    scale_y_continuous(name = "Estimated proportion (+- 90% CI)",
                       limits = c(-0.15, 1.15),
                       breaks = seq(0, 1, 0.2),
                       labels = seq(0, 1, 0.2),
                       sec.axis = sec_axis(~ ., 
                                           name = "",
                                           breaks = seq(0, 1, 0.2),
                                           labels = seq(0, 1, 0.2)
                                           )
                       ) +
    geom_hline(yintercept = 3, color = "grey", linetype = 2) +
    theme(panel.background = element_blank(),
          panel.border = element_rect(color = "black", fill = "NA"),
          axis.line = element_line(),
          axis.text = element_text(color = "black"),
          legend.position = "top",
          plot.title = element_text(hjust = 0.5, size = 12), # Centered and bold with a smaller font size
          plot.title.position = "plot", # Position the title over the plot area
          ) +
    scale_color_manual(values = palette(), name = "Sample") +
    labs(title = "", x = "Category", y = "") +
    theme(plot.margin = margin(0, 0, 0, 0)) +
  facet_wrap(Profile_label ~ Sample) +
  scale_x_continuous(labels = c("not\nconducted",
                              "teacher\nexperiment",
                              "student\nexperiment",
                              "can't\nremember"))

ggsave("RQ5_Learning.png", dpi = 450, width = 12, height = 8)



```


## Wissenschaftliches Denken und Experimentiererfahrung

Experiment not implemented, implemented as student experiment, implemented as teacher experiment, or can’t remember.


```{r}

summary()

d %>% select(demo_exp, schuel_exp) %>% summary()
d %>% select(demo_exp) %>% table()
d %>% select(schuel_exp) %>% table()

d %>% select(demo_exp, schuel_exp, Repko_score, Konzept_score) %>% cor(use = "pairwise.complete.obs")

#scientific thinking

#Stellt diese Vis. wissch Modell dar?
d %>% select(wiss_1) %>% table() #Hälfte ja, Hälfte nein

#Bildet gesamtes Magnetfeld des Hufeisenmagneten ab?

d %>% select(wiss_2) %>% table() #90% nein, 10% ja

#Warum bildet nicht ganzes ab?
#Weil...
#nur bei einem Experiment relevante Aspekte werden abgebildet
d %>% select(wiss_3_1) %>% table() #90% ja, 10% nein
#Es wäre möglich, das ganze Magnetfeld abzubilden
d %>% select(wiss_3_2) %>% table() #55% ja, 45% nein
#Abbildung des gesamtes Magnetfeldes wäre sinnvoll
d %>% select(wiss_3_3) %>% table() #25% ja, 75% nein

d %>% select(wiss_4_1) %>% table() #Wssch Mod zeigt alle Eigensch des Originals; bisschen

d %>% select(wiss_4_2) %>% table() #Wssch Mod ist identisch mit Original; eher nicht

d %>% select(wiss_4_3) %>% table() #Wssch Mod ist exakte Kopie der Realität; fast gar nicht

d %>% select(wiss_4_4) %>% table() #Wssch Mod ist in Aussehen und Funktion mit Original genau gleich; bisschen

d %>% select(wiss_4_5) %>% table() #Wssch Mod stellt Realität korrekt dar; eher schon recht ja

d %>% select(wiss_4_1:wiss_4_5) %>% summary()
d %>% select(wiss_4_1:wiss_4_5) %>% ggpairs(., lower = list(continuous = my_descriptivesfunction))

d %>% select(wiss_1:wiss_4_5) %>% summary()
d %>% select(wiss_3_2:wiss_3_3) %>% table()
table(d$wiss_7_a)
d$wiss_7_b
d %>% select(wiss_7_a:wiss_7_b) %>% write.csv(file = "wissschdk_cvsundbegr.csv")


d %>% select(demo_exp:leit_exp,
             Repko_score,
             Konzept_score) %>%
  cor(use = "pairwise.complete.obs")
d %>% select(leit_exp, Konzept_score) %>% ggplot(aes(leit_exp, Konzept_score)) +
  geom_smooth() +
  geom_point(position = position_jitter())
d %>% ggplot(aes(leit_exp_f, Konzept_score)) +
  geom_boxplot()

#Demo: 1-5
#Schüler:1-5
#Leit_exp: Nein, als Demo-Exp., als Schüler-Exp., Weiss nicht mehr
#PROBLEM: Leute ohne Experiment: Wissen nicht, ob Thema überhaupt unterrichtet? Typischerweise schon...

summary(lm(Konzept_score ~ leit_exp_f, data = d))
summary(lm(Repko_score ~ leit_exp_f, data = d))

summary(lm(scale(Konzept_score) ~ scale(Repko_score)*leit_exp_f, data = d))

#Dimensionen Repko:
#Punkt und Feld (aber beides Vektor/Vektorfeld)
#Oder: Betrag und Richtung

#Item 4 repko:
#4a-4c: Alles richtig um 1 Punkt zu bekommen? (im Moment: 0-4 für a-d)
d %>% select(repko_4a_erg,
             repko_4b_erg,
             repko_4c_erg,
             repko_4d_erg) %>%
  cor(use = "pairwise.complete.obs")

#Repko Item 5: A bic C in einen Punkt stecken.


d %>% select(wiss_4_1:wiss_4_5, Repko_score, Konzept_score) %>%
  ggpairs(., lower = list(continuous = my_descriptivesfunction))

d %>% select(Modell, Repko_score, Konzept_score) %>%
  ggpairs(., lower = list(continuous = my_descriptivesfunction))

summary(lm(Repko_score ~ Konzept_score*leit_exp_f + Konzept_score*Modell, data = d))

summary(lm(Repko_score ~ Konzept_score*Modell, data = d))
summary(lm(Repko_score ~ Konzept_score*leit_exp_f, data = d))
```

```{r}

table(d$repko_4a)
table(d$repko_4b)
table(d$repko_4c)

table(d$repko_4a, d$leit_exp_f)
table(d$repko_4b, d$leit_exp_f)
table(d$repko_4c, d$leit_exp_f)
table(d$repko_4d, d$leit_exp_f)
table(d$repko_4d)
table(d$repko_6)

```

### Data preprations and exclusions

```{r datapreps.exclusions}

##Data samples 1-4
d14 <- readxl::read_xlsx("D14.xlsx")

##Data sample 5 (ETH Physics freshmen)
d_nurETH <- readxl::read_xlsx("nur_ETH.xlsx")

##Align variable types within both datasets to enable merging
d14$quota_assignment <- as.double(d14$quota_assignment)
d_nurETH$quota_assignment <- as.double(d_nurETH$quota_assignment)
d14$ats <- as.double(d14$ats)
d_nurETH$ats <- as.double(d_nurETH$ats)

##Merge
d <- bind_rows(d14, d_nurETH)

##Indicate ETH sample
d$Datensatz[is.na(d$Datensatz)] <- 5

##Add ID variable (ID according to row number)
d$ID <- rownames(d)

##Export students' ID and explanations why they indicated that their data are not trustworthy for external inspection
#d %>% select(DQ, Kom, ID) %>% filter(DQ == 3) %>% write.table(file = "C:/local user data/Antrag_Physik/Analysen_2020-11-11/Kom.dat")

##Exclude participants who indicated that their data are not trustworthy (DQ == 3) and who did not explain this choice simply with lack of knowledge (whom our rule would be to include)
d_exclusions <- d %>% filter(ID != "28" &
              ID != "122" &
              ID != "147" &
              ID != "219" &
              ID != "235" &
              ID != "245" &
              ID != "249" &
              ID != "266" &
              ID != "281" &
              ID != "296" &
              ID != "340" &
              ID != "341" &
              ID != "385" &
              ID != "391" &
              ID != "401" &
              ID != "441" &
              ID != "457" &
              ID != "468" &
              ID != "478" &
              ID != "535") %>%
  filter(duration == -1 | duration > 600)

dim(d_exclusions) #We now have, after the exclusions, 515 students left - so, 25 have been excluded overall

##If this is all fine: Overwrite former dataset-object
d <- d_exclusions

##check data object
str(d)
names(d)
dim(d)

##correct data errors

##a "5" on the leit_exp-variable was a data error
d <- d %>%
  mutate(leit_exp = na_if(leit_exp, 5)) %>%
  mutate(leit_exp_f = as.factor(leit_exp), #factor whether and how they engaged in Leitschaukel-Experiment
         Modell = rowMeans(d %>% select(wiss_4_1:wiss_4_5), na.rm = TRUE) #Modellverstaendnis-Gesamtmittelwert
         )

#Gender (1 = female, 2 = male)
d$d_sex[d$d_sex == 0] <- NA
d$d_sex[d$d_sex == 3] <- NA
d$d_sex <- d$d_sex - 1 #Now sex is scores as 0 = female, 1 = male
d$male <- d$d_sex


d %<>% mutate(d_geb = na_if(d_geb, -99)) %>%
  mutate(d_geb = na_if(d_geb, 1)) %>%
  mutate(d_geb = na_if(d_geb, 420)) %>%
  mutate(d_geb = na_if(d_geb, 2020)) %>%
    mutate(d_geb = na_if(d_geb, 97))
# %>%
#  mutate(d_geb = recode(d_geb, '97' = "1997"))

```

### Score-production

```{r}
##compute representational competence item scores
d <- d %>%
  mutate(repko_4a_erg = recode(repko_4a, '1' = 1, .default = 0),
         repko_4b_erg = recode(repko_4b, '1' = 0, .default = 1),
         repko_4c_erg = recode(repko_4c, '1' = 0, .default = 1),
         repko_4d_erg = recode(repko_4d, '1' = 0, .default = 1),
         repko_5a_erg = recode(repko_5a, '1' = 1, .default = 0),
         repko_5b_erg = recode(repko_5b, '1' = 1, .default = 0),
         repko_5c_erg = recode(repko_5c, '1' = 0, .default = 1)) %>%
  mutate(repko_4_sum = rowSums(.[, c("repko_4a_erg", "repko_4b_erg", "repko_4c_erg")]),
         repko_5_sum = rowSums(.[, c("repko_5a_erg", "repko_5b_erg", "repko_5c_erg")])) %>%
  mutate(repko_1_erg = recode(repko_1, '1' = 1, .default = 0),
         repko_2_erg = recode(repko_2, '3' = 1, .default = 0),
         repko_3_erg = recode(repko_3, '5' = 1, .default = 0),
         repko_4_erg = recode(repko_4_sum, '3' = 1, .default = 0),
         repko_5_erg = recode(repko_5_sum, '3' = 1, .default = 0),         
         repko_6_erg = recode(repko_6, '4' = 1, .default = 0),
         repko_7_erg = recode(repko_7, '2' = 1, .default = 0),
         repko_8_erg = recode(repko_8, '2' = 1, .default = 0),
         repko_9_erg = recode(repko_9, '4' = 1, .default = 0),
         repko_10_erg = recode(repko_10, '6' = 1, .default = 0),
         repko_11_erg = recode(repko_11, '5' = 1, .default = 0),
         repko_12_erg = recode(repko_12, '1' = 1, .default = 0))

##compute representational competence sum, percentage, and z-scores
 d <- d %>% mutate(Repko_score = rowSums(d %>%
                                 select(repko_1_erg:repko_12_erg)))

##compute conceptual knowledge item scores
d <- d %>%
  mutate(konzept_2_erg = recode(konzept_2, '5' = 1, .default = 0),
         konzept_3_erg = recode(konzept_3, '1' = 1, .default = 0),
         konzept_4_erg = recode(konzept_4, '2' = 1, .default = 0),
         konzept_5_erg = recode(konzept_5, '4' = 1, .default = 0),
         konzept_7_erg = recode(konzept_7, '2' = 1, .default = 0),
         konzept_8_erg = recode(konzept_8, '5' = 1, .default = 0),
         konzept_9_erg = recode(konzept_9, '4' = 1, .default = 0),
         konzept_10_erg = recode(konzept_10, '4' = 1, .default = 0),
         konzept_11_erg = recode(konzept_11, '3' = 1, .default = 0),
         konzept_12_erg = recode(konzept_12, '7' = 1, .default = 0),
         konzept_13_erg = recode(konzept_13, '6' = 1, .default = 0),
         konzept_14_erg = recode(konzept_14, '5' = 1, .default = 0),
         konzept_15_erg = recode(konzept_15, '4' = 1, .default = 0))

##compute conceptual knowledge sum, percentage, and z-scores
d <- d %>%  mutate(Konzept_score = rowSums(d %>%
                                 select(konzept_2_erg:konzept_15_erg) %>% select(-konzept_11_erg)))

d %<>% mutate(male_factor = factor(male))

d$Repko_score_q <- d$Repko_score^2

d$Repko_score_cent <- scale(d$Repko_score, scale = FALSE)
d$Repko_score_cent_q <- d$Repko_score_cent^2

df <- d %>% filter(male == 0) 
dm <- d %>% filter(male == 1) 

```

## Some descriptives & Intercorrelations

```{r descs1}

d %>% select(Repko_score, Konzept_score, Repko_prop, Konzept_prop) %>% describe


#c(-99, 1, 97, 420, 2020)
d$d_geb
describe(d %>% select(d_sex, d_geb) %>% mutate(d_geb_2020 = 2020 - d_geb))

table(d$d_sex)

#212? 200?
  
  table(d$d_sex, d$Datensatz)
names(d)

table(d$Datensatz)
View(d)
d %>% select(Datensatz, d_Studium) %>% View()



```


```{r  internal.consistencies}

d %>% select(repko_1_erg:repko_12_erg) %>% omega(poly = TRUE, nfactors = 1)
#Omega = .86; Alpha = .86

d %>% select(konzept_2_erg:konzept_15_erg) %>% select(-konzept_11_erg) %>% omega(poly = TRUE, nfactors = 1)
#Omega = .92; Alpha = .91

```


## RQ3 LPA MG Step 3 STD

```{r RQ3.LPA.MG_STEP3_STD}

LPA_RQ3_MG_STEP3_STD <- '


TITLE:
CESAR03_RQ3_LPA_Multigroup_3profiles_STEP3_STD;

DATA:
FILE IS
"C:/local user data/CESAR0.3/Analysis_R/CESAR03.dat";

VARIABLE:

NAMES =
ID
Repko
Konzept
sample
male
leit_exp
teacher
MINT
;

USEVARIABLES ARE
repko konzept
;

CLASSES = s(4) c(3);
knownclass = s(sample = 1 sample = 2 sample = 3 sample = 4);

MISSING = all(9999);

DEFINE:
standardize REPKO KONZEPT;

ANALYSIS:

TYPE = mixture;
STARTS 1000 400;
PROCESS = 4 1;

MODEL:

%OVERALL%

C ON S;

%s#1.c#1%

[repko*] (m1);
[konzept*] (m2);
repko* (v1);
konzept* (v2);

%s#2.c#1%

[repko*] (m1);
[konzept*] (m2);
repko* (v1);
konzept* (v2);

%s#1.c#2%

[repko*] (m3);
[konzept*] (m4);
repko* (v3);
konzept* (v4);

%s#2.c#2%

[repko*] (m3);
[konzept*] (m4);
repko* (v3);
konzept* (v4);

%s#1.c#3%

[repko*] (m5);
[konzept*] (m6);
repko* (v5);
konzept* (v6);

%s#3.c#1%

[repko*] (m5);
[konzept*] (m6);
repko* (v5);
konzept* (v6);



%s#2.c#3%

[repko*] (m7);
[konzept*] (m8);
repko* (v7);
konzept* (s2v8);

%s#4.c#1%

[repko*] (m7);
[konzept*] (m8);
repko* (v7);
konzept* (s2v8);


%s#3.c#2%

[repko*] (m9);
[konzept*] (m10);
repko* (v9);
konzept* (v10);

%s#3.c#3%

[repko*] (m11);
[konzept*] (m12);
repko* (v11);
konzept* (v12);


%s#4.c#2%

[repko*] (m13);
[konzept*] (m14);
repko* (v13);
konzept* (v14);

%s#4.c#3%

[repko*] (m15);
[konzept*] (m16);
repko* (v15);
konzept* (v16);

OUTPUT: sampstat residual tech1;

plot:
type is plot1 plot2 plot3;
series is repko (1) konzept (2);

'

```

### RQ3 LPA MG STEP3_STD: Run analyses of created models MG

```{r run.dataanalyses.MG}
dir.create("CESAR03_RQ3_LPA_Multigroup_STEP3_STD")

writeLines(LPA_RQ3_MG_STEP3_STD, "CESAR03_RQ3_LPA_Multigroup_STEP3_STD/LPA_RQ3_MG_STEP3_STD.inp")

#Run Mplus input files
runModels(target = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ3_LPA_Multigroup_STEP3_STD/", recursive = TRUE)

```

### RQ3 LPA MG STEP3_STD: Inspect results

```{r LPA.results.MG.STEP3_STD}

RQ3_LPAs_MG_STEP3_STD_outputs <- readModels(target = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ3_LPA_Multigroup_STEP3_STD/", what = c("summaries", "parameters", "class_counts", "lcCondMeans"), recursive = TRUE)

RQ3_LPAs_MG_STEP3_STD_outputs$parameters$unstandardized %>%
  filter(paramHeader == "Means") %>%
  filter(param == "KONZEPT" | param == "REPKO") %>%
  mutate(param = fct_relevel(param,
                             c("REPKO", "KONZEPT"))) %>%
  mutate(param = fct_recode(param,
                            "Representational Competence" = "REPKO",
                            "Conceptual Knowledge" = "KONZEPT")) %>%
  mutate(Sample = substr(LatentClass, 1, 1),
         Profile = substr(LatentClass, 3, 3)) %>%
    mutate(Sample = fct_recode(factor(Sample),
                             "Teacher Education SU" = "1",
                             "Engineering TUK" = "2",
                             "Environmental Science ETH" = "3",
                             "Physics ETH" = "4")) %>%
 mutate(LatentClass_labels = fct_recode(LatentClass,
                                  "RC low/CK low" = "1.1",
                                  "RC low/CK low" = "2.1",
                                  "RC below average/CK below average" = "1.2",
                                  "RC below average/CK below average" = "2.2",
                                  "RC high/CK above average" = "1.3",
                                  "RC high/CK above average" = "3.1",
                                  "RC above average/CK high" = "2.3",
                                  "RC above average/CK high" = "4.1",
                                  "RC high/CK high" = "4.3",
                                  "RC average/CK low" = "3.3",
                                  "RC below average/CK average" = "3.2",
                                  "RC below average/CK below average" = "4.2")) %>%
  ggplot(aes(x = param, y = est, group = LatentClass, color = Sample, shape = LatentClass_labels)) +
  geom_line(position = position_dodge(width = 0.05), size = 1) +
  geom_point(position = position_dodge(width = 0.05), size = 2) +
  geom_errorbar(aes(ymin = est - 1.68*se, ymax = est + 1.68*se), width = 0.1,
                position = position_dodge(width = 0.05)) +
  theme_bw() +
  scale_color_manual(values = palette()) +
  xlab("") +
  ylab("Estimate +- 90% CI")

ggsave("RQ3_MG_STEP3_STD_Profiles.png", width = 7, height = 4, dpi = 450)


describe(CESAR03$Repko_score)
Repko_mean <- 6.38
Repko_sd <- 2.90
describe(CESAR03$Konzept_score)
Konzept_mean <- 3.60
Konzept_sd <- 3.19

RQ3_LPAs_MG_STEP3_outputs$parameters$unstandardized %>%
  filter(paramHeader == "Means") %>%
  filter(param == "KONZEPT" | param == "REPKO") %>%
  mutate(param = fct_relevel(param,
                             c("REPKO", "KONZEPT"))) %>%
  mutate(param = fct_recode(param,
                            "Representational Competence" = "REPKO",
                            "Conceptual Knowledge" = "KONZEPT")) %>%
  mutate(Sample = substr(LatentClass, 1, 1),
         Profile = substr(LatentClass, 3, 3)) %>%
    mutate(Sample = fct_recode(factor(Sample),
                             "Teacher Education SU" = "1",
                             "Engineering TUK" = "2",
                             "Environmental Science ETH" = "3",
                             "Physics ETH" = "4")) %>%
  mutate(LatentClass_labels = fct_recode(LatentClass,
                                  "RC low/CK low" = "1.1",
                                  "RC low/CK low" = "2.1",
                                  "RC below average/CK below average" = "1.2",
                                  "RC below average/CK below average" = "2.2",
                                  "RC high/CK above average" = "1.3",
                                  "RC high/CK above average" = "3.1",
                                  "RC above average/CK high" = "2.3",
                                  "RC above average/CK high" = "4.1",
                                  "RC high/CK high" = "4.3",
                                  "RC average/CK low" = "3.3",
                                  "RC below average/CK average" = "3.2",
                                  "RC below average/CK below average" = "4.2")) %>%
  ggplot(aes(x = param, y = est, group = LatentClass, color = Sample, shape = LatentClass_labels)) +
  geom_line(position = position_dodge(width = 0.05), size = 1) +
  geom_point(position = position_dodge(width = 0.05), size = 2) +
  geom_errorbar(aes(ymin = est - 1.68*se, ymax = est + 1.68*se), width = 0.1,
                position = position_dodge(width = 0.05)) +
  theme_bw() +
  scale_color_manual(values = palette()) +
  xlab("") +
  ylab("Estimate +- 90% CI")

ggsave("RQ3_MG_STEP3_Profiles_labels.png", width = 7, height = 4, dpi = 450)


## RQ3 LPA MG Step 3 ROBSCALED

```{r RQ3.LPA.MG_STEP3_ROBSCALED}

LPA_RQ3_MG_STEP3_ROBSCALED <- '


TITLE:
CESAR03_RQ3_LPA_Multigroup_3profiles_STEP3_ROBSCALED;

DATA:
FILE IS
"C:/local user data/CESAR0.3/Analysis_R/CESAR03_robscaled.dat";

VARIABLE:

NAMES =
ID
Repko
Konzept
sample
male
leit_exp
teacher
MINT
;

USEVARIABLES ARE
repko konzept
;

CLASSES = s(4) c(3);
knownclass = s(sample = 1 sample = 2 sample = 3 sample = 4);

MISSING = all(9999);

ANALYSIS:

TYPE = mixture;
STARTS 1000 400;
PROCESS = 4 1;

MODEL:

%OVERALL%

C ON S;

%s#1.c#1%

[repko*] (m1);
[konzept*] (m2);
repko* (v1);
konzept* (v2);

%s#2.c#1%

[repko*] (m1);
[konzept*] (m2);
repko* (v1);
konzept* (v2);

%s#1.c#2%

[repko*] (m3);
[konzept*] (m4);
repko* (v3);
konzept* (v4);

%s#2.c#2%

[repko*] (m3);
[konzept*] (m4);
repko* (v3);
konzept* (v4);

%s#1.c#3%

[repko*] (m5);
[konzept*] (m6);
repko* (v5);
konzept* (v6);

%s#3.c#1%

[repko*] (m5);
[konzept*] (m6);
repko* (v5);
konzept* (v6);



%s#2.c#3%

[repko*] (m7);
[konzept*] (m8);
repko* (v7);
konzept* (s2v8);

%s#4.c#1%

[repko*] (m7);
[konzept*] (m8);
repko* (v7);
konzept* (s2v8);


%s#3.c#2%

[repko*] (m9);
[konzept*] (m10);
repko* (v9);
konzept* (v10);

%s#3.c#3%

[repko*] (m11);
[konzept*] (m12);
repko* (v11);
konzept* (v12);


%s#4.c#2%

[repko*] (m13);
[konzept*] (m14);
repko* (v13);
konzept* (v14);

%s#4.c#3%

[repko*] (m15);
[konzept*] (m16);
repko* (v15);
konzept* (v16);

OUTPUT: sampstat residual tech1;

plot:
type is plot1 plot2 plot3;
series is repko (1) konzept (2);

'

```

### RQ3 LPA MG STEP3_STD: Run analyses of created models MG

```{r run.dataanalyses.MG}
dir.create("CESAR03_RQ3_LPA_Multigroup_STEP3_ROBSCALED")

writeLines(LPA_RQ3_MG_STEP3_ROBSCALED, "CESAR03_RQ3_LPA_Multigroup_STEP3_ROBSCALED/LPA_RQ3_MG_STEP3_ROBSCALED.inp")

#Run Mplus input files
runModels(target = "./CESAR03_RQ3_LPA_Multigroup_STEP3_ROBSCALED/", recursive = TRUE)

```

### RQ3 LPA MG STEP3_ROBSCALED: Inspect results

```{r LPA.results.MG.STEP3_ROBSCALED}

RQ3_LPAs_MG_STEP3_ROBSCALED_outputs <- readModels(target = "C:/local user data/CESAR0.3/Analysis_R/CESAR03_RQ3_LPA_Multigroup_STEP3_ROBSCALED/", what = c("summaries", "parameters", "class_counts", "lcCondMeans"), recursive = TRUE)

RQ3_LPAs_MG_STEP3_ROBSCALED_outputs$parameters$unstandardized %>%
  filter(paramHeader == "Means") %>%
  filter(param == "KONZEPT" | param == "REPKO") %>%
  mutate(param = fct_relevel(param,
                             c("REPKO", "KONZEPT"))) %>%
  mutate(param = fct_recode(param,
                            "Representational Competence" = "REPKO",
                            "Conceptual Knowledge" = "KONZEPT")) %>%
  mutate(Sample = substr(LatentClass, 1, 1),
         Profile = substr(LatentClass, 3, 3)) %>%
    mutate(Sample = fct_recode(factor(Sample),
                             "Teacher Education SU" = "1",
                             "Engineering TUK" = "2",
                             "Environmental Science ETH" = "3",
                             "Physics ETH" = "4")) %>%
 mutate(LatentClass_labels = fct_recode(LatentClass,
                                  "RC low/CK low" = "1.1",
                                  "RC low/CK low" = "2.1",
                                  "RC below average/CK below average" = "1.2",
                                  "RC below average/CK below average" = "2.2",
                                  "RC high/CK above average" = "1.3",
                                  "RC high/CK above average" = "3.1",
                                  "RC above average/CK high" = "2.3",
                                  "RC above average/CK high" = "4.1",
                                  "RC high/CK high" = "4.3",
                                  "RC average/CK low" = "3.3",
                                  "RC below average/CK average" = "3.2",
                                  "RC below average/CK below average" = "4.2")) %>%
  ggplot(aes(x = param, y = est, group = LatentClass, color = Sample, shape = LatentClass_labels)) +
  geom_line(position = position_dodge(width = 0.05), size = 1) +
  geom_point(position = position_dodge(width = 0.05), size = 2) +
  geom_errorbar(aes(ymin = est - 1.68*se, ymax = est + 1.68*se), width = 0.1,
                position = position_dodge(width = 0.05)) +
  theme_bw() +
  scale_color_manual(values = palette()) +
  xlab("") +
  ylab("Estimate +- 90% CI") +
 # scale_y_continuous(limits = c(0, 1),
#                     breaks = seq(0, 1, 0.1),
#                     sec.axis = sec_axis( trans=~., name="Estimate", breaks = seq(0, 1, 0.1)))
  scale_y_continuous(limits = c(-1, 1.5),
                     breaks = seq(-1, 1.5, 0.5),
                     sec.axis = sec_axis( trans=~., name="Estimate", breaks = seq(-1, 1.5, 0.5)))

ggsave("RQ3_MG_STEP3_HALFLOGROBSCALED_Profiles.png", width = 7, height = 4, dpi = 450)


```


```
